Forecasting interrupted time series

### 2024-02-19 fits.qmd
Keywords

---
title: "Forecasting interrupted time series"
author:
- name: Rob J Hyndman
  affiliations:
    - department: Department of Econometrics & Business Statistics
    - name: Monash University
    - city: Clayton VIC
    - country: Australia
    - postal-code: 3800
  email: Rob.Hyndman@monash.edu
  corresponding: true
- name: Bahman Rostami-Tabar
  affiliations:
    - name: Cardiff Business School
    - postal-code: Wales CF10 3EU
    - country: United Kingdom
  email: rostami-tabarb@cardiff.ac.uk
abstract: "Forecasting interrupted time series data is a major challenge for forecasting teams, especially in light of events such as the COVID-19 pandemic. This paper investigates several strategies for dealing with interruptions in time series forecasting, including highly adaptable models, intervention models, marking interrupted periods as missing, forecasting what may have been, downweighting the interruption period, and ensemble models.  Each approach offers specific advantages and disadvantages, such as adaptability, memory retention, data integrity, flexibility, and accuracy. We evaluate the effectiveness of these strategies using two actual datasets that were interrupted by COVID-19, and we provide recommendations for how to handle these interruptions. This work contributes to the literature on time series forecasting, offering insights for academics and practitioners dealing with interrupted data in numerous domains."
keywords: "Forecasting, interrupted time series, disruptive events, COVID-19"
bibliography: references.bib
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: false
linestretch: 1.5
format:
  wp-pdf:
    include-in-header: header.tex
    keep-tex: true
---

>>>>

---
title: "Forecasting interrupted time series"
author:
- name: Rob J Hyndman
  affiliations:
    - department: Department of Econometrics & Business Statistics
    - name: Monash University
    - city: Clayton VIC
    - country: Australia
    - postal-code: 3800
  email: Rob.Hyndman@monash.edu
  corresponding: true
- name: Bahman Rostami-Tabar
  affiliations:
    - name: Cardiff Business School
    - postal-code: Wales CF10 3EU
    - country: United Kingdom
  email: rostami-tabarb@cardiff.ac.uk
abstract: "Forecasting interrupted time series data is a major challenge for forecasting teams, especially in light of events such as the COVID-19 pandemic. This paper investigates several strategies for dealing with interruptions in time series forecasting, including highly adaptable models, intervention models, marking interrupted periods as missing, forecasting what may have been, downweighting the interruption period, and ensemble models.  Each approach offers specific advantages and disadvantages, such as adaptability, memory retention, data integrity, flexibility, and accuracy. We evaluate the effectiveness of these strategies using two actual datasets that were interrupted by COVID-19, and we provide recommendations for how to handle these interruptions. This work contributes to the literature on time series forecasting, offering insights for academics and practitioners dealing with interrupted data in numerous domains."
keywords:
  - counterfactual forecasting
  - COVID-19
  - disruptive events
  - intervention analysis
  - structural breaks
bibliography: references.bib
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: false
linestretch: 1.5
format:
  wp-pdf:
    include-in-header: header.tex
    keep-tex: true
---
